%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Education}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cventries}

%------------------------------------------------

\cventry
{Advisor: Prof. Biman Bagchi} % Degree
{PhD (Statistical Physics), Indian Institute of Science} % Institution
{Bengaluru, India} % Location
{Aug. 2009 - Apr. 2014} % Date(s)
{ % Description(s) bullet points
\begin{cvitems}
\item {Diffusion equation for a rugged potential energy landscape.}
\item {Understanding the origin of long-range hydrophobic force.}
\item {Role of biological water in the hydration shell of proteins.}
\item {Hydrophobicity and composition-dependent anomalies in aqueous binary mixtures.}
\item {Administration and maintenance of high performance computing (HPC) cluster from Sep. 2011 to Apr. 2015.}
\end{cvitems}
}

\cventry
{Advisor: Prof. Biman Bagchi} % Degree
{M.S. (Chemistry), Indian Institute of Science} % Institution
{Bengaluru, India} % Location
{Aug. 2007 - Jun. 2009} % Date(s)
{ % Description(s) bullet points
\begin{cvitems}
\item {Relevant Courses: Statistical Physics, Physical Chemistry, Thermodynamics, Basic probability theory.}
\item {Class rank 2\sst{nd} with a CGPA of 6.9 out of 8.}
\end{cvitems}
}

\cventry
{Ramakrishna Mission Vidyamandira} % Degree
{B.Sc., University of Calcutta} % Institution
{Calcutta, India} % Location
{Aug. 2004 - May 2007} % Date(s)
{ % Description(s) bullet points
\begin{cvitems}
\item {Major in chemistry, with physics and mathematics as auxiliary subjects.}
\item {Ranked 1\sst{st} in the University of Calcutta.}
\end{cvitems}
}

%------------------------------------------------

\end{cventries}
