%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Experience}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cventries}

%------------------------------------------------

\cventry
{Postdoctoral Research Associate \quad\textbar\quad Advisor: Dr. Johannes S{\"o}ding} % Job title
{Max Planck Institute for Biophysical Chemistry} % Organization
{G{\"o}ttingen, Germany} % Location
{May 2015 -- Present} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Developed a Bayesian methodology and software for large scale analyses of medical data.}
\item {Communicated our method in an international peer-reviewed journal as the first author of a research article.}
\item {Presented our work at an international conference (ISMB 2019). Invited to speak at the University of G{\"o}ttingen.}
\item {Coordinated a project to develop a software for analysing large scale transcriptomics data. Communication in progress.}
\item {Supervised a Master's thesis and mentored three internship students. Three students are now pursuing higher studies at reputed international institutes in Canada, United States and Australia. Another student is working at PWC, Switzerland.}
%\item {Method development and analyses of medical data to understand the genetic origin of common, non-infectious diseases.}
%\item {Public speaking for professional audience, teaching and mentoring for students.}
%\item {B-LORE: a software for post-GWAS analyses using Bayesian multiple logistic regression with variable selection.}
%\item {TEJAAS: a high-throughput method for detecting trans-eQTLs.}
\end{cvitems}
}

%------------------------------------------------    

\cventry
{Research Associate \quad\textbar\quad Advisor: Prof. Biman Bagchi} % Job title
{Indian Institute of Science} % Organization
{Bengaluru, India} % Location
{May 2014 - Apr. 2015} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Led two projects with challenging deadlines and international collaborations: (1) Understanding the origin of long-range hydrophobic force, and (2) Role of biological water in the hydration shell of proteins.}
\item {Communicated both of them in international peer-reviewed journals, one of them as first author.}
\item {In charge of administration and maintenance of high performance computing (HPC) cluster from Sep. 2011 to Apr. 2015.}
\end{cvitems}
}

%------------------------------------------------

\cventry
{A B2B company for word-of-mouth marketing} % Job title
{Co-founder, Beejig} % Organization
{Bengaluru, India} % Location
{Jan. 2012 - Sep. 2013} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Extensively involved in conceptualization, market research and app development.}
\item {Raised initial funding of \$20000 and recruited sales manager along with a team of two sales executives.}
\item {Deployed our marketing tool for Lakme India chain of salons in Bengaluru. Their sales increased by 22\% in only two months, and we were invited to launch our program in Mumbai.}
\item {Organized the dissolution of our company by selling the assets to a bigger company.}
\end{cvitems}
}

%------------------------------------------------

\end{cventries}
