%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Experience}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cventries}

%------------------------------------------------

\cventry
{Advisor: Dr. Johannes S{\"o}ding} % Job title
{Postdoctoral Fellow, Max Planck Institute for Biophysical Chemistry} % Organization
{G{\"o}ttingen, Germany} % Location
{Jun. 2015 -- Present} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Developed three statistical methods for understanding disease mechanism from large scale biomedical data.
       Technical details: (1) Bayesian multiple logistic regression for finemapping in post-GWAS analysis, (2) large-scale trans-eQTL discovery from RNA-Seq data, (3) Bayesian multi-omics approach to combine GWAS and eQTL data.}
\item {Communicated and collaborated with medical doctors leading to a first author publication.}
\item {Presented our work at an international conference (ISMB 2019). Invited to speak at the University of G{\"o}ttingen.}
\item {Supervised a Master's thesis and mentored three internship students.}
%\item {Method development and analyses of medical data to understand the genetic origin of common, non-infectious diseases.}
%\item {Public speaking for professional audience, teaching and mentoring for students.}
%\item {B-LORE: a software for post-GWAS analyses using Bayesian multiple logistic regression with variable selection.}
%\item {TEJAAS: a high-throughput method for detecting trans-eQTLs.}
\end{cvitems}
}

%------------------------------------------------    

\cventry
{Advisor: Prof. Biman Bagchi} % Job title
{Research Associate, Indian Institute of Science} % Organization
{Bengaluru, India} % Location
{Aug. 2014 - May 2015} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Led two projects with challenging deadlines: (1) Understanding the origin of long-range hydrophobic force, and (2) Role of biological water in the hydration shell of proteins.}
\item {Communicated both of them in international peer-reviewed journals, one of them as first author.}
\item {In charge of administration and maintenance of high performance computing (HPC) cluster from Aug. 2011 to May 2015.}
\end{cvitems}
}

%------------------------------------------------

\cventry
{A B2B company for word-of-mouth marketing} % Job title
{Co-founder, Beejig} % Organization
{Bengaluru, India} % Location
{Jan. 2013 - Feb. 2014} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Extensively involved in conceptualization, market research and app development.}
\item {Raised initial funding of \$20000 and recruited sales manager along with a team of two sales executives.}
\item {Deployed our marketing tool for Lakme India chain of salons in Bengaluru. Their sales increased by 12\% in only two months, and we were invited to launch our program in Mumbai.}
\item {Organized the dissolution of our company by selling the assets to a bigger company.}
\end{cvitems}
}

%------------------------------------------------

\end{cventries}
